The assessment of the ability of measurements, nowcasts, and forecasts to track changes

### 2024-04-21 paper.tex
Change affiliations / contributions

\affil[1]{\orgdiv{Institute for Operations Research}, \orgname{Karlsruhe Institute of Technology (KIT)}, \orgaddress{\street{Kaiserstr. 12}, \city{Karlsruhe}, \postcode{76131}, \country{Germany}}}
%TC:ignore
\abstract{ 
Measurements, nowcasts, or forecasts ideally should correctly reflect changes in the values of interest.
In this article, we focus on how to assess the ability of measurements, nowcasts, or forecasts to correctly predict the direction of changes in values – which we refer to as the ability to track changes. 
We present visual techniques and quantitative measures to assess the ability to track changes and provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
We exemplarily illustrate the proposed methods to assess the ability to track changes for nowcasting during the COVID-19 pandemic, patient admissions to an emergency department, and non-invasive blood pressure measurements.
}
%TC:endignore
\keywords{}

@@

OG, BL, and JR developed the theoretical formalism.
BL and JR implemented the methods.
JR conducted the simulations and analyzed the data.
BL and JR wrote the manuscript.
All authors discussed the results, critically reviewed them, and contributed to the final manuscript.

>>>>

\affil[1]{\orgdiv{Institute for Operations Research}, \orgname{Karlsruhe Institute of Technology (KIT)}, \orgaddress{\street{Kaiserstr. 12}, \city{Karlsruhe}, \postcode{76131}, \country{Germany}}}
\affil[2]{\orgdiv{Department of Anesthesiology, Center of Anesthesiology and Intensive Care Medicine}, \orgname{University Medical Center Hamburg-Eppendorf}, \orgaddress{\street{Martinistrasse 52}, \city{Hamburg}, \postcode{20246}, \country{Germany}}}
%TC:ignore
\abstract{ 
Measurements, nowcasts, or forecasts ideally should correctly reflect changes in the values of interest.
In this article, we focus on how to assess the ability of measurements, nowcasts, or forecasts to correctly predict the direction of changes in values – which we refer to as the ability to track changes. 
We present visual techniques and quantitative measures to assess the ability to track changes and provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
We exemplarily illustrate the proposed methods to assess the ability to track changes for nowcasting during the COVID-19 pandemic, patient admissions to an emergency department, and non-invasive blood pressure measurements.
}
%TC:endignore
\keywords{}

@@

JR, BL, and OG developed the theoretical formalism.
JR and BL implemented the methods.
JR conducted the simulations and analyzed the data.
All authors interpreted the data.
BS and OG substantively revised the manuscript.
JR and BL drafted the manuscript.
All authors have approved the submitted version and have agreed both to be personally accountable for the author's own contributions and to ensure that questions related to the accuracy or integrity of any part of the work, even ones in which the author was not personally involved, are appropriately investigated, resolved, and the resolution documented in the literature.
